xsface - file length sanity checking

### 2018-01-10 analysis-main/main_analyses_bll.Rmd
integrated last detectors, reran sanity checks, added face size analyses

```{r}
rm(list=ls())
library(readr)
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(lubridate)
```

Note that the dataset here is those participants (31) who pass the length sanity checks.

```{r}
d <- read_csv("../data/consolidated_data_passing.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))
demo <- read_csv("../data/demographics/demographics.csv")
#cdis <- read_csv("../data/cdis/cdi_summary.csv") ## not in repo
```

@@

```{r}
mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face)) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len))))

@@

ggplot(mss, aes(x = factor(age.grp), y = face, col = posture)) +
  geom_boxplot() +
  ylab("Proportion Face Detections") +
  xlab("Age (months)") +
  facet_grid(~orientation) +
  ylim(c(0,.2)) +
  theme_bw()
```

@@

```{r}
namings <- d %>%
  group_by(subid) %>%
  do(summarize.naming(.)) %>%
  left_join(demo %>% select(subid, gender, age.at.test, len))
```

@@

```{r}
naming_rate <- namings %>%
  group_by(subid, age.grp, age.at.test) %>%
  summarise(num = n(),
            len = len[1]) %>%
  mutate(rate = num / as.numeric(as.duration(lubridate::hms(len)) / dminutes())) # bll edits here to wrangle dates

@@

```{r}
naming_rate_familiarity <- namings %>%
  group_by(subid, familiarity, age.at.test) %>%
  summarise(num = n(),
            len = len[1]) %>%
  mutate(rate = num / as.numeric(as.duration(lubridate::hms(len)) / dminutes())) # bll edits here to wrangle dates

@@

```{r}
namings %>%
  group_by(subid, name, familiarity, age.at.test) %>%
  summarise(num = n(),
            len = len[1]) %>%
  mutate(rate = num / as.numeric(as.duration(lubridate::hms(len)) / dminutes())) %>%  # bll edits here to wrangle dates
  ggplot(aes(x = age.at.test, y = rate, col = name)) +
  geom_point() +
  facet_grid(.~familiarity) +
  geom_smooth(span = 1) +
  ylab("Namings per minute") +
  xlab("Age (months)") +
  theme_bw()
```

@@

```{r}
library(plyr)

  sb <- ddply(d,~subid, summarize.naming, window=c(-3,0))
  sa <- ddply(d,~subid, summarize.naming, window=c(0,3))
  sb$window <- "before"
  sa$window <- "after"
  s <- rbind(sb,sa)
  s$window <- factor(s$window)

@@

<!-- ## How do face detections change with sequence of naming instances? -->

<!-- ```{r} -->
<!-- ms <- namings %>% -->
<!--   group_by(age.grp, subid, naming.instance, familiarity, name) %>% -->
<!--   summarise(face = mean(face)) %>% -->
<!--   group_by(age.grp, naming.instance, familiarity) %>% -->
<!--   multi_boot_standard(col = "face", na.rm = TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ggplot(ms, -->
<!--        aes(x = naming.instance, y = mean, col = familiarity)) + -->
<!--   geom_point() + -->
<!--   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + -->
<!--   geom_smooth(se = FALSE) + -->
<!--   facet_grid(~age.grp) + -->
<!--   xlim(c(0,20)) + -->
<!--   scale_color_solarized() + -->
<!--   theme_bw() -->
<!-- ``` -->

>>>>

```{r}
rm(list=ls())
library(readr)
library(plyr) # need to load this for scripts, always load before
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(lubridate)
```

Note that the dataset here is now the complete data (N=36); all pass length sanity checks.

```{r}
d <- read_csv("../data/consolidated_data.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))
demo <- read_csv("../data/demographics/demographics.csv")
#cdis <- read_csv("../data/cdis/cdi_summary.csv") ## not in repo
```

@@

```{r}
mss <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face)) %>%
  left_join(demo) %>%
  # mutate(len = as.numeric(lubridate::as.duration(lubridate::ms(len)))) ## error here, used simpler calculation.
  mutate(len = as.numeric(len_seconds/60))

@@

ggplot(mss, aes(x = factor(age.grp), y = face, col = posture)) +
  geom_boxplot() +
  ylab("Proportion Face Detections") +
  xlab("Age (months)") +
  facet_grid(~orientation) +
  ylim(c(0,.2)) +
  theme_bw()
```
# Face area: descriptives, posture and orientation
## When detected, how much of the field of view did faces occupy? (% of screen)

```{r}
screenPixels=720 * 480
d$faceArea = d$w * d$h /screenPixels

mss <- d %>%
  group_by(age.grp, subid) %>%
  summarise(faceArea = mean(faceArea, na.rm="TRUE")) %>%
  group_by(age.grp)

ms <- mss %>%
  multi_boot_standard(col = "faceArea")

ggplot(mss, aes(x = age.grp, y = faceArea)) + 
  geom_jitter(width = .25) + 
  geom_pointrange(data = ms, 
                 aes(x = age.grp, 
                     y = mean, 
                     ymin = ci_lower, 
                     ymax = ci_upper), col = "red") +
  geom_line(data = ms, 
             aes(x = age.grp, 
                     y = mean), col = "red") + 
  scale_x_continuous(breaks=c(8,12,16)) +
  ylab("% ScreenArea of Face Detections") + 
  xlab("Age (months)") + 
  theme_bw() 
```

## Face size as a function of continous age

```{r}
mssFaceArea <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(faceArea = mean(faceArea, na.rm="TRUE")) %>%
  left_join(demo) %>%
  mutate(len = as.numeric(len_seconds/60))

ggplot(mssFaceArea, aes(x = age.at.test, y = faceArea)) + 
  geom_jitter(width = .25, aes(size = len)) + 
  geom_smooth() + 
  scale_x_continuous(breaks=c(8,12,16)) +
  scale_size_continuous(name = "Length (s)") + 
  ylab("% Area of Face Detections") + 
  xlab("Age (months)") + 
  theme_bw() 
```

## Face size by infant's posture

```{r}
mss <- d %>%
  filter(!is.na(posture)) %>%
  filter(!is.na(face)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(faceArea = mean(faceArea, na.rm="TRUE")) %>%
  group_by(age.grp)

# ms <- mss %>%
#   multi_boot_standard(col = "faceArea")

ggplot(mss, aes(x = factor(age.grp), y = faceArea, col = posture)) + 
  geom_boxplot() + 
  ylab("% Area of Face Detections") + 
  xlab("Age (months)") + 
  theme_bw() 
```

## Face Area by Caregiver Orientation
```{r}
mss <- d %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid) %>%
  summarise(faceArea = mean(faceArea, na.rm="TRUE")) %>%
  group_by(age.grp)

# ms <- mss %>%
#   multi_boot_standard(col = "faceArea")

ggplot(mss, aes(x = factor(age.grp), y = faceArea, col = orientation)) + 
  geom_boxplot() + 
  ylab("% Area of Face Detections") + 
  xlab("Age (months)") + 
  theme_bw() 
```

@@

```{r}
namings <- d %>%
  group_by(subid) %>%
  do(summarize.naming(.)) %>%
  left_join(demo %>% select(subid, gender, age.at.test, len_seconds))
```

@@

```{r}
naming_rate <- namings %>%
  group_by(subid, age.grp, age.at.test) %>%
  summarise(num = n(),
            len = len_seconds[1]) %>%
  mutate(rate = num / as.numeric(len / 60)) # bll edits here to wrangle dates

@@

```{r}
naming_rate_familiarity <- namings %>%
  group_by(subid, familiarity, age.at.test) %>%
  summarise(num = n(),
            len = len_seconds[1]) %>%
  mutate(rate = num / as.numeric(len / 60)) # bll edits here to wrangle dates

@@

```{r}
namings %>%
  group_by(subid, name, familiarity, age.at.test) %>%
  summarise(num = n(),
            len = len_seconds[1]) %>%
  mutate(rate = num / as.numeric(len / 60)) %>%  # bll edits here to wrangle dates
  ggplot(aes(x = age.at.test, y = rate, col = name)) +
  geom_point() +
  facet_grid(.~familiarity) +
  geom_smooth(span = 1) +
  ylab("Namings per minute") +
  xlab("Age (months)") +
  theme_bw()
```

@@

```{r}
sb <- plyr::ddply(d,~subid, summarize.naming, window=c(-2,0)) ## used 2 second window as in ms draft
sa <- plyr::ddply(d,~subid, summarize.naming, window=c(0,2))

sb$window <- "before"
sa$window <- "after"
s <- rbind(sb,sa)
s$window <- factor(s$window)

@@

## How do face detections change with sequence of naming instances?

```{r}
ms <- namings %>%
  group_by(age.grp, subid, naming.instance, familiarity, name) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp, naming.instance, familiarity) %>%
  multi_boot_standard(col = "face", na.rm = TRUE)
```

```{r}
ggplot(ms,
       aes(x = naming.instance, y = mean, col = familiarity)) +
  geom_point() +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(se = FALSE) +
  facet_grid(~age.grp) +
  xlim(c(0,20)) +
  scale_color_solarized() +
  theme_bw()
```

### 2018-01-10 analysis-validation/length_sanity_check.Rmd
integrated last detectors, reran sanity checks, added face size analyses

```{r}
demo <- read_csv("../data/demographics/demographics.csv")
movies <- read_csv("../data/video_stats/new_movie_lengths.csv") 
dets <- read_csv("../data/final_output/mtcnn2.csv")
```

>>>>

```{r}
demo <- read_csv("../data/demographics/demographics.csv")
movies <- read_csv("../data/video_stats/new_movie_lengths.csv") 
dets <- read_csv("../data/final_output/mtcnn3.csv")
```
